Atomify - a live LAMMPS visualizer

### 2017-03-04 ms.tex
Fix footnote

\section{Introduction}
%
Molecular dynamics (MD) is a common technique for simulating the motion of atoms
and molecules in a broad range of fields.
% TODO does MD also include larger particles?
% TODO which fields?
Over the years, increasingly sophisticated methods have been developed.
% TODO what methods?
With the large number of force fields, advanced techniques and GPU acceleration,
implementing a good molecular dynamics simulation is a challenging task.
There are many software packages for molecular dynamics modelling
available
\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}.
Some packages, such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}
have been developed for more than two decades and contain more than one million
lines of code each.

>>>>

\section{Introduction}
%
Molecular dynamics (MD) is a common technique for simulating the motion of atoms
and molecules in a broad range of fields.
% TODO does MD also include larger particles?
% TODO which fields?
Over the years, increasingly sophisticated methods have been developed.
% TODO what methods?
With the large number of force fields, advanced techniques and GPU acceleration,
implementing a good molecular dynamics simulation is a challenging task.
There are many software packages for molecular dynamics modelling
available
\footnote{See \url{https://en.wikipedia.org/wiki/Comparison_of_software_for_molecular_mechanics_modeling}.}
Some packages, such as LAMMPS\cite{plimpton1995fast} and GROMACS\cite{Pronk2013}
have been developed for more than two decades and contain more than one million
lines of code each.
